A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-19 main.tex
TCIA return

%注意 強調GSE2837: 
%The prognostic significance of the candidate genes has been validated by an independent patient cohort.
% validation by GSE2837 cohort (with web-tools)
%\subsubsection*{GSE2837} % non-TCGA
% from Anwser2-2
%by GEO GSE2837 HNSCC dataset (PrognoScan)
After the discovery with our workflow, we validated the suggested 20 biomarkers in the other independent \acrshort{hnscc} cohort (GSE2837).
The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
%17 out of 20 candidates
%?DKK1 (0.253635), 
%Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
The 10 out of 20 candidates are confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort. Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.

@@

\subsubsection{Table3/legend} Table 3

@@

\subsubsection{Table4/legend} Table 4

@@

>>>>

%注意 強調GSE2837: 
%The prognostic significance of the candidate genes has been validated by an independent patient cohort.
% validation by GSE2837 cohort (with web-tools)
%\subsubsection*{GSE2837} % non-TCGA
% from Anwser2-2
%by GEO GSE2837 HNSCC dataset (PrognoScan)
After the discovery by our workflow, we validated the suggested 20 biomarkers in the other independent \acrshort{hnscc} cohort (GSE2837).
The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
%17 out of 20 candidates
%?DKK1 (0.253635), 
%Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
The 10 out of 20 candidates have been confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort. Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.

@@

%\subsubsection{Table3/legend} Table 3

@@

%\subsubsection{Table4/legend} Table 4

@@

%***

\subsubsection{TCIA validation by deep learning}
%https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
%https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Pytorch/Keras framework)
%數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。

OFA:  TCIA for whole slide deep learning
IL19 is a candidate marker
TCPA modeling: Y (RNA-seq) ← X (slide represents gene expression)
Apply model on TMUH HNSCC test cohort (with survival outcome):
Y (survival) ← X (slide represents gene expression)
(as IL19 validation, to see is it still a biomarker)
%x The Stanford Tissue Microarray Database (TMAD; x http://tma.stanford.edu) 
%https://tma.im/cgi-bin/ontologyBrowser.pl?anchor=C34447; there is few HNSCC slides

%Manning meap book: 不再是黑盒子
%https://www.manning.com/books/trust-in-machine-learning
Trust in Machine Learning *** interpretable or explainable CNN
By saliency mapping: e.x. diabetes retinopathy, model focused on retinal artery
%https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
%#XAI
Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data\cite{Hao2019a}
By PyTorch

%https://www.deeplearningbook.org/
image-based phenotypes could be correlated with their underlying genomics data 
TMA by deep learning (CNN) mRNA expression associated with pathological images
*** TCGA TCIA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, digital TMA
%https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
%https://github.com/Serian1992/ImgBio.
%https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
% NCI
Aiding the Genomics Characterization of Tumors: 
deep learning could predict commonly mutated genes and mRNA expression from the images
*** A deep learning model to predict RNA-Seq expression of tumours from whole slide images\cite{Schmauch2020}
Preprocessing of whole-slide images. The application of deep-learning algo- rithms to histological data is a challenging problem, particularly due to the high dimensionality of the data (up to 100,000 × 100,000 pixels for a single whole-slide image) and the small size of available datasets. We divided the whole-slide images into squares of 112 × 112 $\mu$m (224 × 224 pixels) called “tiles”, and used the Otsu algorithm62 (as implemented in python package skimage) to select only those containing tissue, excluding the white background. We sampled a maximum of 8000 such tiles from each slide. We then extracted 2048 features from those tiles with a 50-layer ResNet63 pretrained on the ImageNet dataset64 (using the Keras implementation), such that a slide could be represented as a 8000 × 2048 matrix.
For the first phase of this work (transcriptome prediction), we accelerated the training of our models through a simple preprocessing step inspired by simple linear iterative clustering (SLIC)65: we used the k-means algorithm (as implemented in python package libkmcuda) to create 100 clusters (supertiles) of tiles on the basis of tile location on the slide, and we averaged the features of the tiles within each cluster. The use of these supertiles reduces the dimensions of a slide to 100 × 2048. The model was first trained on this reduced dataset, with all the TCGA data. Then, for specific organs, fine-tuning was achieved with full-scale data from the organs concerned only.

%AI methods can also be used to identify specific gene mutations from tumor pathology images instead of using traditional genomic sequencing. For instance, NCI-funded researchers at New York University used deep learning (DL) to analyze pathology images of lung tumors obtained from The Cancer Genome Atlas. Not only could the DL method accurately distinguish between two of the most common lung cancer subtypes, adenocarcinoma and squamous cell carcinoma, it could predict commonly mutated genes from the images.

Understanding the Method Behind the Machine: interpredability

%One challenge of AI, and DL specifically, is the “black box” problem: not fully understanding what features of the data a computer has used in its decision-making process. For example, a DL algorithm that predicts the optimal treatment for a patient does not provide the reasoning it used to make that prediction. Additional efforts are needed to reveal how algorithms arrive at a decision or prediction so that the process becomes transparent to scientists and clinicians. Making these algorithms transparent could help researchers identify new biological features relevant to disease diagnosis or treatment.
***  unconscious biases:
Incorporating information about biological processes into the algorithm is likely to improve its accuracy and decrease dependence on large amounts of annotated data, which may not be available. One danger of the “black box” problem is that DL may inadvertently perpetuate existing unconscious biases. Researchers need to carefully consider how potential biases affect the data being used to develop a model, adopt practices to address and monitor those biases, and monitor performance and applicability of AI models.

%With increased investments, NCI’s efforts to realize AI’s potential will lead to more accurate and rapid diagnoses, improved clinical decision-making, and, ultimately, better health outcomes for patients with cancer and those at risk. Updated: August 31, 2020
%
